A model-based method for detecting persistent cultural change using panel data[^thanks]

### 2021-02-08 ms.Rmd
final resubmission

---
title: A model-based method for detecting persistent cultural change using panel data[^thanks]
author:
  - Stephen Vaisey[^SV]
  - Kevin Kiley[^KK]
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
# header-includes:
#   - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 11pt
---

>>>>

---
title: A model-based method for detecting persistent cultural change using panel data[^thanks]
author:
  - Stephen Vaisey[^SV]
  - Kevin Kiley[^KK]
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    keep_tex: true
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
# header-includes:
#   - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 11pt
---
